Hadoop Image Processing Framework

### 2015-03-15 Paper.tex
Finished editing algorithm descriptions.

\section{Image Processing Computations}
To address the framework capability, we considered to take some existing well used image processing algorihtms and enable running its functionality on a hadoop cluster. These considerations led us to a development of image processing functionality in java for the following computations: flat field correction, canny edge detection and image segmentation. These computations are computationally intensive and data intensive which are operated on range from hundreds to hundred thousands of images. Next we categorize these three computations

@@

\subsection{Laplacian Filter}
The Laplacian is a 2-D isotropic measure of the 2nd spatial derivative of an image. The Laplacian of an image highlights regions of rapid intensity change and is therefore often used for edge detection. The Laplacian is often applied to an image that has first been smoothed with something approximating a Gaussian smoothing filter in order to reduce sensitivity to noise. The operator normally takes a single gray level image as input and produces another gray level image as output.

@@

Since the input image is represented as a set of discrete pixels, we have to find a discrete convolution kernel that can approximate the second derivatives in the definition of the Laplacian. This a simplest computation that consists of few additions and multiplications.

\subsection{Canny Edge Detection}
Canny Edge Detection\cite{Canny86} is an multi-stage algorithm to detect a wide range of edges in images. Edge detection, especially step edge detection is an important technique to extract useful structural information from different vision objects and dramatically reduce the amount of data to be processed. Among the edge detection methods developed so far, canny edge detection algorithm is one of the most strictly defined methods that provides good and reliable detection.

The process of Canny edge detection algorithm can be broken down to 5 different stages:

\begin{itemize}
	\item Apply Gaussian filter to smooth the image in order to remove the noise.
	\item Find the intensity gradients of the image.
	\item Apply non-maximum suppression to get rid of spurious response to edge detection
	\item Apply double threshold to determine potential edges.
	\item Track edge by hysteresis. Finalize the detection of edges by suppressing all the other edges that are weak and not connected to strong edges. 
\end{itemize}

\subsection{Image segmentation using k-means clustering}
K-Means algorithm is an unsupervised clustering algorithm that classifies the input data points into multiple classes based on their inherent distance from each other. The algorithm assumes that the data features form a vector space and tries to find natural clustering in them. The points are clustered around centroids \begin{math}\mu_{i} \forall i = 1...k\end{math} which are obtained by minimizing the objective
\begin{equation}
	V = \sum\limits_{i=1}^n \sum\limits_{x_{j}\in S_{i}} (x_{j} - \mu_{i})^2
\end{equation}

where there are \begin{math}k\end{math} clusters \begin{math} S_{i},i=1,2,...,k \end{math} and \begin{math} \mu_{i} \end{math} is the centroid or mean point of all the points \begin{math}x_{j} \in S_{i}\end{math}

As a part of the experiment, an iterative version of the algorithm was implemented. The algorithm takes a 2 dimensional image as input. Various steps in the algorithm are as follows:

\begin{itemize}
	\item Compute the intensity distribution(also called the histogram) of the intensities.
	\item Initialize the centroids with k random intensities.
	\item Repeat the following steps until the cluster labels of the image does not change anymore.
	\item Cluster the points based on distance of their intensities from the centroid intensities.
	\begin{equation}
		c^{i} := arg min_{j}||x^{i} - \mu_{j}||^2
	\end{equation}
	\item Compute the new centroid for each of the clusters.
	\begin{equation}
		\mu_{i} = \frac{\sum\limits_{i=1}^{m} 1\{c_{i} = j\}x^i}{\sum\limits_{i=1}^{m} 1\{c_{i} = j\}}
	\end{equation}

	where \begin{math}k\end{math} is a parameter of the algorithm (the number of clusters to be found), \begin{math}i\end{math} iterates over that all the intensities, \begin{math}j\end{math} iterates over all the centroids and \begin{math}\mu_{i}\end{math} are the centroid intensities.
\end{itemize}

>>>>

\section{Image Processing Computations}
To explore the Hadoop Image Processing Framework's capabilities and
performance, we implemented multiple variations of existing
widely-used image processing algorithms:
\begin{itemize}
\item A stand-alone implementation running on a single node with no
  distributed processing capability
\item A generic Hadoop implementation which requires a high level of
  software engineering expertise within the Hadoop framework
\item An implementation that employs the Hadoop Image Processing
  Framework
\end{itemize}

We chose the following algorithms: Laplacian filtering, Canny edge
detection and $k$-means image segmentation.  These are widely-used,
computation- and data-intensive algorithms of varying complexity which
require large distributed systems for timely operation on hundreds of
thousands of images.

@@

\subsection{Laplacian Filter}
The Laplacian is a 2-D isotropic measure of the 2nd spatial derivative
of an image. The Laplacian of an image highlights regions of rapid
intensity change and is therefore often used for edge detection. The
Laplacian is often applied to an image that has first been smoothed
with an approximation of a Gaussian filter in order to reduce
sensitivity to noise. The operator normally takes a single gray level
image as input and produces another gray level image as output.

@@

Since the input image is represented as a set of discrete pixels, we
have to find a discrete convolution kernel that can approximate the
second derivatives in the definition of the Laplacian. This is a very
simple computation that consists of a few additions and
multiplications.

\subsection{Canny Edge Detection}
Canny edge detection\cite{Canny86} is an multi-stage algorithm to
detect a wide range of edges in images. Edge detection, especially
step edge detection, is an important technique to extract useful
structural information from visual information, dramatically reducing
the amount of data to be processed. Among existing edge detection
methods, the Canny edge detection algorithm is considered to provide
reliable edge detection without relying on context-specific
heuristics.

The process of the Canny edge detection algorithm can defined in five
stages:

\begin{itemize}
\item Apply a Gaussian filter to smooth the image and remove noise.
\item Find the intensity gradients of the image.
\item Apply non-maximum suppression to get rid of spurious
  responses to edge detection
\item Apply a double threshold to determine potential edges.
\item Track edges by hysteresis. Finalize the detection of
  edges by suppressing all edges that are ``weak'' and not
  connected to strong edges.
\end{itemize}

\subsection{Image segmentation using $k$-means clustering}
The $k$-means algorithm is an unsupervised clustering algorithm that
classifies input data points into multiple classes based on their
Euclidean distance from each other. The algorithm assumes that the
data features form a vector space and tries to find natural
clusterings within it. The points are clustered around
centroids \begin{math}\mu_{i} \forall i = 1...k\end{math} which are
  obtained by minimizing the objective
\begin{equation}
	V = \sum\limits_{i=1}^n \sum\limits_{x_{j}\in S_{i}} (x_{j} - \mu_{i})^2
\end{equation}

where there are \begin{math}k\end{math} clusters \begin{math}
    S_{i},i=1,2,...,k \end{math} and \begin{math} \mu_{i} \end{math}
  is the centroid or mean point of all the points \begin{math}x_{j}
    \in S_{i}\end{math}.

For the purposes of our experiment, we implemented iterative versions
of the algorithm. The algorithm takes a 2-dimensional image as
input. The steps of the algorithm are as follows:

\begin{itemize}
\item Compute the intensity distribution (also called the
  histogram) of the image.
\item Initialize the centroids with $k$ random intensities.
\item Repeat the following steps until the cluster labels of
  the image stop changing from one iteration to the next:
  \begin{itemize}
  \item Cluster the points based on the distance of their intensities
    from the centroid's intensity.
	\begin{equation}
		c^{i} := \mbox{argmin}_{j}||x^{i} - \mu_{j}||^2
	\end{equation}
	\item Compute the new centroid for each of the clusters.
	\begin{equation}
		\mu_{i} = \frac{\sum\limits_{i=1}^{m} 1\{c_{i} = j\}x^i}{\sum\limits_{i=1}^{m} 1\{c_{i} = j\}}
	\end{equation}

	where \begin{math}k\end{math} is a parameter of the algorithm
          (the number of clusters to be
          found), \begin{math}i\end{math} iterates over all the
            intensities, \begin{math}j\end{math} iterates over all the
              centroids and \begin{math}\mu_{i}\end{math} are the
              centroid intensities.
  \end{itemize}
\end{itemize}
